---
title: "9w2RmarkdownAndLeaflet"
author: "Bleile"
date: "8/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Executive Summary

This script will be saved as .rmd to github and through knitr will produce a map of my favorite places using leaflet.

## Instructions
Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 


```{r initialize, echo=FALSE}
#setup
#Load packages
pacman::p_load(pacman, dplyr, GGally, ggplot2, ggthemes, ggvis, lubridate, plotly, rio, markdown, shiny, tidyverse, leaflet)

```
## R Markdown and Leaflet
```{r mapping, echo = TRUE}
library(leaflet)
my_map <- leaflet() |> addTiles() 
my_favs <- data.frame(name=c("Bemmel", "Taytay", "Belfair", "Pemba", "Stockholm", "Virginia Beach", "Tubli", "Bali", "Mazatlan"),
                      lat = c(51.892601, 14.562280, 47.450851, -4.915833, 59.332790, 36.850769, 26.188910, -8.455470, 23.200630), 
                      lng = c(5.896940, 121.147370, -122.827431, 39.679069, 18.064489, -76.285873, 50.552680, 115.071579, -106.421516))
                 
my_map |>
leaflet() |> addTiles() |> addMarkers(my_favs$lng, my_favs$lat, popup=my_favs$name)
```
## My Favorite Places as of 14 August, 2021

